Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-12-13 paper.tex
Citations directly follow names; resolves #64

Blackwell et al. investigated the effects of Reynolds number on the performance
of a 2 m diameter Darrieus vertical-axis cross-flow wind turbine with NACA 0012
blades \cite{Blackwell1976}. By varying wind tunnel speed, the turbine was made
to operate at approximately constant blade chord Reynolds number $Re_c$ ranging
from $1 \times 10^5$ to $3 \times 10^5$. In this regime the turbine power
coefficient $C_P$ was shown to be sensitive to $Re_c$, with sensitivity
diminishing at the higher Reynolds numbers, especially for turbines of lower
solidity ($Nc/R$, where $N$ is the number of blades and $R$ is the turbine's
maximum radius). More recently, Polagye and Cavagnaro observed significant
Reynolds number sensitivity for a high solidity helical cross-flow turbine
\cite{Polagye2013b}, and Bravo et al. observed power coefficient of a
straight-bladed VAWT to become Reynolds number independent at $Re_c \approx 4
\times 10^5$ \cite{Bravo2007}. Bachant and Wosnik \cite{Bachant2014} first
observed Reynolds number independence of power coefficient at optimal tip speed
ratio for a high solidity cross-flow turbine at $Re_D \approx 10^6$ or
$Re_{c,\mathrm{avg}} \approx 2 \times 10^5$.

@@

Krogstad and Adaramola observed Reynolds number independence of the performance
of a 0.9 m diameter axial-flow turbine rotor at $Re_D \approx 5 \times 10^5$ in
wind tunnel tests \cite{Krogstad2012a}. Their turbine blades had an S826 profile
along their entire span, a profile chosen for its $Re$-independence. Walker et
al. \cite{Walker2014} similarly chose a NACA 63-618 foil for their axial-flow
turbine tests in a towing tank, which were performed at a mid-span Reynolds
number $Re_c = 4 \times 10^5$. McTavish et al. \cite{McTavish2013} showed how
the near-wake expansion for an axial-flow rotor is increased at higher Reynolds
numbers, concluding that physical models should be designed with
$Re$-independence in mind if they are to be run at low $Re$.

>>>>

Blackwell et al. \cite{Blackwell1976} investigated the effects of Reynolds
number on the performance of a 2 m diameter Darrieus vertical-axis cross-flow
wind turbine with NACA 0012 blades. By varying wind tunnel speed, the turbine
was made to operate at approximately constant blade chord Reynolds number $Re_c$
ranging from $1 \times 10^5$ to $3 \times 10^5$. In this regime the turbine
power coefficient $C_P$ was shown to be sensitive to $Re_c$, with sensitivity
diminishing at the higher Reynolds numbers, especially for turbines of lower
solidity ($Nc/R$, where $N$ is the number of blades and $R$ is the turbine's
maximum radius). More recently, Polagye and Cavagnaro \cite{Polagye2013b}
observed significant Reynolds number sensitivity for a high solidity helical
cross-flow turbine, and Bravo et al. \cite{Bravo2007} observed power coefficient
of a straight-bladed VAWT to become Reynolds number independent at $Re_c \approx
4 \times 10^5$. Bachant and Wosnik \cite{Bachant2014} first observed Reynolds
number independence of power coefficient at optimal tip speed ratio for a high
solidity cross-flow turbine at $Re_D \approx 10^6$ or $Re_{c,\mathrm{avg}}
\approx 2 \times 10^5$.

@@

Krogstad and Adaramola \cite{Krogstad2012a} observed Reynolds number
independence of the performance of a 0.9 m diameter axial-flow turbine rotor at
$Re_D \approx 5 \times 10^5$ in wind tunnel tests. Their turbine blades had an
S826 profile along their entire span, a profile chosen for its
$Re$-independence. Walker et al. \cite{Walker2014} similarly chose a NACA 63-618
foil for their axial-flow turbine tests in a towing tank, which were performed
at a mid-span Reynolds number $Re_c = 4 \times 10^5$. McTavish et al.
\cite{McTavish2013} showed how the near-wake expansion for an axial-flow rotor
is increased at higher Reynolds numbers, concluding that physical models should
be designed with $Re$-independence in mind if they are to be run at low $Re$.
